IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-15 paper/real.tex
reviewer 2: is string too restrictive

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\paragraph{Server-side IFC for Node.js:}
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatment, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Fig.~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
We remark that our system conservatively restricts
the kinds of messages that can be exchanged, via |send| (and |sandbox|),
to string values.
%
(We provide a convenience library which marshalls JSON objects to/from strings.)
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%

>>>>

\begin{figure}[t]
\centerline{\includegraphics[width=0.7\columnwidth]{figs/node}}
\caption{\label{fig:node}
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced (right).}
\end{figure}
%
\paragraph{Server-side IFC for Node.js:}
We have implemented |specLangJS seqf| for Node.js in the form of a
library, without modifying Node.js or the V8 JavaScript engine.
%
Our implementation\footnote{Available at \codelink{}.} provides a
library for creating new tasks, i.e., contexts whose global object
only contains the standard JavaScript library and our IFC primitives
(e.g., |send| and |sandbox|).
%
When mapped to our formal treatment, |sandbox| is defined with |ap
klone tS = tS0|, where |tS0| is the global object corresponding to the
standard JavaScript library and our IFC primitives.
%
%These tasks can communicate and create new tasks, in turn.
%
These IFC operations are mediated by the trusted library code (executing
as the main Node.js context), which tracks the state (current label, messages,
etc.) of each task.  An example for |send|/|recv| is shown in
Fig.~\ref{fig:node}.
%While V8 provides a means for sharing any object between contexts (used
%by same-origin contexts in Blink),
Our system conservatively restricts the kinds of messages that can be
exchanged, via |send| (and |sandbox|), to string values.
%
%
In our formalization, this amounts to restricting the IFC language rule
for |send| in the following way:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
Of course, we provide a convenience library which marshals JSON
objects to/from strings.
%
We remark that this is not unlike existing message-passing JavaScript
APIs, e.g., \texttt{postMessage}, which impose similar restrictions as
to avoid sharing references between concurrent code.
